Optimizing the power of adaptive seamless designs using Bayesian Optimization

### 2020-10-21 main.tex
grid7 ...

As explained before, we obtained unbiased results from the exhaustive grid search and the MBO procedure.
Figure~\ref{fig:plot_boxplot_valid_y} shows that \emph{MBO} yields better results for each effect set even though \emph{MBO} is just allowed 116 evaluations in contrast to the 1350 evaluations that are conducted by the \emph{grid search}.
\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{generated/figures/plot_boxplot_valid_y.pdf}
\caption{%
  Validated performance of both approaches.
  }
\label{fig:plot_boxplot_valid_y}
\end{figure}
The difference in the number of evaluations is also reflected in the average runtime of each optimization methods given in Table~\ref{tab:table_time}.
\input{generated/tables/table_time.tex}
For the chosen grid resoultion and evaluation budget for \emph{MBO}, \emph{MBO} is approxamatly 20-times faster and yields better configurations.

>>>>

As explained before, we obtained unbiased results from the exhaustive grid search and the MBO procedure.
Figure~\ref{fig:plot_boxplot_valid_y} shows that \emph{MBO} yields better results for each effect set even though \emph{MBO} is just allowed 116 evaluations in contrast to the 1350 evaluations that are conducted by the \emph{grid search} (126 by \emph{Grid 7}).
\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{generated/figures/plot_boxplot_valid_y.pdf}
\caption{%
  Validated performance of both approaches.
  }
\label{fig:plot_boxplot_valid_y}
\end{figure}
The difference in the number of evaluations is also reflected in the average runtime of each optimization methods given in Table~\ref{tab:table_time}.
\input{generated/tables/table_time.tex}
For the chosen grid resoultion and evaluation budget for \emph{MBO}, \emph{MBO} is approxamatly 20-times faster and yields better configurations.
